### 2023-08-14 my_paper/Hadah-last-names.tex
submit paper to JODE

@@

\linespread{1}{\title{{\fontfamily{ptm}
\selectfont{\Large{\MakeUppercase{The Impact of Hispanic Last Names and Identity on Labor Market Outcomes}}}}}}
	\author{{\fontfamily{pbk}\selectfont\large{\textsc{Hussain Hadah}}\thanks{Department of Economics, Tulane University, 6823 St. Charles Ave., New Orleans, LA 70118, United States (e-mail: \email{hhadah@tulane.edu}).}}}
	\date{\fontfamily{pbk}\selectfont\normalsize{\textsc{\today}}}
	\maketitle

@@

\input{tables/tab03a-summary-stats-mex}

\input{tables/tab03a-summary-stats-nonmex}

>>>>

% Redefine figure and table counters to use Arabic numerals
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}

@@

\linespread{1}{\title{{\fontfamily{ptm}\selectfont{\Large{\MakeUppercase{The Impact of Hispanic Last Names and Identity on Labor Market Outcomes}}}}
\thanks{I thank Professors Willa Friedman, Chinhui Juhn, Vikram Maheshri, and Yona Rubinstein for their support and advice. I also thank Aimee Chin, Steven Craig, German Cubas, Elaine Liu, Fan Wang, and the participants of the Applied Microeconomics Workshop at the University of Houston.}
}}
	\author{{\fontfamily{pbk}\selectfont\large{\textsc{Hussain Hadah}}\thanks{Department of Economics, Tulane University, 6823 St. Charles Ave., New Orleans, LA 70118, United States, (phone: +1-602-393-8077, e-mail: \email{hhadah@tulane.edu}). Competing interests: The author declares none.}}}
	\date{\fontfamily{pbk}\selectfont\normalsize{\textsc{\today}}}
	\maketitle

@@

% \input{tables/tab03a-summary-stats-mex}

% \input{tables/tab03a-summary-stats-nonmex}
